Cover Letter: Cudele (Paper 306)

### 2018-01-08 paper/sections/0_abstract.tex
paper: typos
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

HPC and data center scale application developers are abandoning POSIX IO
because file system metadata synchronization and serialization overheads of
providing strong consistency and durability are too costly -- and often
unnecessary -- for their applications.  Unfortunately, designing file systems
with weaker consistency or durability excludes applications that rely on
stronger guarantees, forcing developers to re-write their applications or
deploy them on a different system.  We present a framework and API that lets
\oldcomment{clients}\newcomment{administrators} specify their
consistency/durability requirements and dynamically assign them to subtrees in
the same namespace, allowing administrators to optimize subtrees over time and
space for different workloads. \oldcomment{By custom fitting a subtree to a
create-heavy application,} We show similar speedups to related work but more
importantly, \oldcomment{our prototype can custom fit subtrees in the same
namespace to applications common in large data centers, }\newcomment{ we show
performance improvements when we custom fit subtree semantics to applications
such as checkpoint-restart (91.7\(\times\) speedup), user home directories
(0.03 standard deviation from optimal), and users checking for partial results
(2\% \oldcomment{clients}\newcomment{users} overhead).} \oldcomment{ and can
scale to 2\(\times\) as many clients when compared to our baseline system.}

>>>>

HPC and data center scale application developers are abandoning POSIX IO
because file system metadata synchronization and serialization overheads of
providing strong consistency and durability are too costly -- and often
unnecessary -- for their applications.  Unfortunately, designing file systems
with weaker consistency or durability semantics excludes applications that rely on
stronger guarantees, forcing developers to re-write their applications or
deploy them on a different system.  We present a framework and API that lets
\oldcomment{clients}\newcomment{administrators} specify their
consistency/durability requirements and dynamically assign them to subtrees in
the same namespace, allowing administrators to optimize subtrees over time and
space for different workloads. \oldcomment{By custom fitting a subtree to a
create-heavy application,} We show similar speedups to related work but more
importantly, \oldcomment{our prototype can custom fit subtrees in the same
namespace to applications common in large data centers, }\newcomment{ we show
performance improvements when we custom fit subtree semantics to applications
such as checkpoint-restart (91.7\(\times\) speedup), user home directories
(0.03 standard deviation from optimal), and users checking for partial results
(2\% \oldcomment{clients}\newcomment{users} overhead).} \oldcomment{ and can
scale to 2\(\times\) as many clients when compared to our baseline system.}

### 2018-01-08 paper/sections/1_introduction.tex
paper: typos
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% What is HPC doing?
To address this, developers are relaxing the consistency and durability
semantics in the file system because weaker guarantees are sufficient for their
applications. For example, many batch style jobs do not need the strong
consistency that the file system provides, so
BatchFS~\cite{zheng:pdsw2014-batchfs} and DeltaFS~\cite{zheng:pdsw2015-deltafs}
do more client-side processing and merge updates when the job is done.
Developers in these domains are turning to these non-POSIX IO solutions because
their applications are well-understood ({\it e.g.}, well-defined read/write
phases, synchronization only needed during certain phases, workflows describing
computation, etc.) and because these applications wreak havoc on file systems
designed for general-purpose workloads ({\it e.g.}, checkpoint-restart's N:N
and N:1 create patterns~\cite{bent_plfs_2009}).

@@

% What did we do
%\footnote{HDFS itself is not directly evaluated in this paper, although the
%semantics and their performance is explored in~\S\ref{sec:use-case-1}.} 
To address this problem, we present an API and framework that lets developers
dynamically control the consistency and durability guarantees for subtrees in
the file system namespace.  Figure~\ref{fig:subtree-policies} shows a potential
setup in our proposed system where a single global namespace has subtrees for
applications optimized with techniques from different state-of-the-art
architectures.  The HDFS subtree has weaker than strong consistency because it
lets clients read files opened for
writing~\cite{hakimzadeh:dais14-hdfs-consistency}, which means that not all
updates are immediately seen by all clients; the BatchFS and RAMDisk subtrees
are decoupled from the global namespace and have similar consistency/durability
behavior to those systems; and the POSIX IO subtree retains the rigidity of
POSIX IO's strong consistency.  Subtrees without policies inherit the
consistency/durability semantics of the parent and future work will examine
embeddable or inheritable policies.

@@

% Results
The results in this paper pave the way for such a system and confirm the
assertions of ``clean-state" research of decoupled namespaces; specifically
that these techniques drastically improve performance.  We go a step further by
quantifying the costs of merging updates (3.37\(\times\) slowdown) and
maintaining durability (\(2.4\times\) slowdown).  In our prototype,
\newcomment{we also show how to assign subtree semantics for certain
applications such as checkpoint-restart (\(91.7\times\) speedup if consistency
is fully relaxed), user home directories (within a 0.03 standard deviation from
optimal), and end-users checking for partial results (only a 2\% overhead).}
\oldcomment{we get an 8\(\times\) speedup and can scale to twice as many
clients when we assign a more relaxed form of consistency and durability to a
subtree with a create-heavy workload.}  We use Ceph as a prototyping platform
because it is used in cloud-based and data center systems and has a presence in
HPC~\cite{wang:pdsw13-ceph-hpc}.

>>>>

% What is HPC doing?
To address this, developers are relaxing the consistency and durability
semantics in the file system because weaker guarantees are sufficient for their
applications. For example, many HPC batch jobs do not need the strong
consistency that the file system provides, so
BatchFS~\cite{zheng:pdsw2014-batchfs} and DeltaFS~\cite{zheng:pdsw2015-deltafs}
do more client-side processing and merge updates when the job is done.
Developers in these domains are turning to these non-POSIX IO solutions because
their applications are well-understood ({\it e.g.}, well-defined read/write
phases, synchronization only needed during certain phases, workflows describing
computation, etc.) and because these applications wreak havoc on file systems
designed for general-purpose workloads ({\it e.g.}, checkpoint-restart's N:N
and N:1 create patterns~\cite{bent_plfs_2009}).

@@

% What did we do
%\footnote{HDFS itself is not directly evaluated in this paper, although the
%semantics and their performance is explored in~\S\ref{sec:use-case-1}.} 
To address this problem, we present an API and framework that lets developers
dynamically control the consistency and durability guarantees for subtrees in
the file system namespace.  Figure~\ref{fig:subtree-policies} shows a potential
setup in our proposed system where a single global namespace has subtrees for
applications optimized with techniques from different state-of-the-art
architectures.  The BatchFS and RAMDisk subtrees are decoupled from the global
namespace and have similar consistency/durability behavior to those systems;
the HDFS subtree has weaker than strong consistency because it lets clients
read files opened for writing~\cite{hakimzadeh:dais14-hdfs-consistency}, which
means that not all updates are immediately seen by all clients; and the POSIX
IO subtree retains the rigidity of POSIX IO's strong consistency.  Subtrees
without policies inherit the consistency/durability semantics of the parent and
future work will examine embeddable or inheritable policies.

@@

% Results
The results in this paper confirm the assertions of ``clean-state" research of
decoupled namespaces; specifically that these techniques drastically improve
performance.  We go a step further by quantifying the costs of merging updates
(3.37\(\times\) slowdown) and maintaining durability (\(2.4\times\) slowdown).
In our prototype, \newcomment{we also show how to assign subtree semantics for
certain applications such as checkpoint-restart (\(91.7\times\) speedup if
consistency is fully relaxed), user home directories (within a 0.03 standard
deviation from optimal), and end-users checking for partial results (only a 2\%
overhead).} \oldcomment{we get an 8\(\times\) speedup and can scale to twice as
many clients when we assign a more relaxed form of consistency and durability
to a subtree with a create-heavy workload.}  We use Ceph as a prototyping
platform because it is used in cloud-based and data center systems and has a
presence in HPC~\cite{wang:pdsw13-ceph-hpc}.

### 2018-01-08 paper/sections/3_posix_overheads.tex
paper: typos
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

In our examination of the overheads of POSIX IO we benchmark and analyze
CephFS, the file system that uses Ceph's object store ({\it i.e.} RADOS) to
store its data and metadata. \newcomment{In this paper, ``client" is a storage
client or application that interacts with the metadata server, ``administrator"
is a system administrator that configures the storage, and ``end-users"
interact with the file system, via home directories or runtimes.} To show how
the file system behaves under high metadata load we use a create-heavy
workload.  During this process we discovered, based on the analysis and
breakdown of costs, that durability and consistency have high overhead but we
urge the reader to keep in mind that this file system is an implementation of
one set of design decisions and our goal here is to highlight the effect that
those decisions have on performance.

Figure~\ref{fig:overhead-creates} shows the resource utilization of compiling
the Linux kernel in a CephFS mount.  The \texttt{untar} phase, which is
characterized by many creates, has the highest resource usage (combined CPU,
network, and disk) because of the number of RPCs needed for consistency and
durability. The RPCs are also serialized because the metadata server is single
threaded; although na\"{\i}ve, this design is common because of the complexity
of multi-threaded metadata
servers~\cite{konstantinos:pdsw2014-lustre-metadata}.  In this section, we
quantify the costs of consistency and durability in CephFS.  At the end of each
subsection we compare the approach to ``decoupled namespaces", the technique in
related work that detaches subtrees from the global namespace to relax
consistency/durability guarantees.

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.32\linewidth}
      \centering
      \includegraphics[width=1\linewidth]{graphs/slowdown-journal.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/baseline-durability/visualize/viz.ipynb}{source}]
      effect of journal} \label{fig:overhead-a}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
      \centering
      \includegraphics[width=0.98\linewidth]{graphs/slowdown-interfere-scale.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/baseline-creates/visualize/viz.ipynb}{source}]
      interference hurts variability}
      \label{fig:overhead-b}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
      \centering
      \includegraphics[width=1.15\linewidth]{graphs/behavior-interfere.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/baseline-interfere/visualize/viz.ipynb}{source}]
      interference increases RPCs}
      \label{fig:overhead-c}
  \end{subfigure}
  \caption{\newcomment{The durability and strong consistency slowdown of the
existing CephFS implementation increases as the number of clients scales.
Results in (a) and (b)  are normalized to 1 client that creates 100K files in
isolation.  (a) shows the effect of journaling metadata updates; ``segment(s)"
is the number of journal segments dispatched to disk at once. (b) shows the
slowdown when another client interferes by creating files in all directories
and (c) highlights the cause: }\oldcomment{The overhead of durability and
strong consistency in CephFS. (a) shows the effect of different journal segment
sizes, which are streamed into the object store for fault tolerance. (b) and
(c) show that} when another client ``interferes", capabilities are revoked and
metadata servers do more work.} \label{fig:overhead}
\end{figure*}

@@

% - sequential IO, trim redundant operations
\textbf{CephFS Design}: A journal of metadata updates that streams into the
resilient object store. Similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL} the metadata journal is designed to be large (on
the order of MBs) which ensures (1) sequential writes into the object store and
(2) the ability for daemons to trim redundant or irrelevant journal entries.
The journal is striped over objects where multiple journal updates can reside
on the same object. There are two tunables\newcomment{, related to groups of
journal events called segments,} for controlling the journal: the segment size
and the dispatch size ({\it i.e.} the number of segments that can be dispatched
at once).  Unless the journal saturates memory or CPU resources, larger values
for these tunables results in better performance.

@@

% Effects on performance
Figure~\ref{fig:overhead-a} shows the effect of journaling with different
\oldcomment{segment sizes; the larger the segment size the bigger that the
writes into the object store are}\newcomment{dispatch sizes, normalized to 1
client that creates 100K files with journaling off (about 654 creates/sec). In
this case a dispatch size of 10 degrades performance the most because the
metadata server is overloaded with requests and cannot spare cycles to manage
concurrent segments.  Tuning and parameter sweeps show that a dispatch size of
10 is the worst and that larger sizes approach a dispatch size of 1; for all
future journal experiments we use a dispatch size of 40 which is a more
realistic configuration.  Although the ``no journal" curve appears flat, it is
actually a slowdown of about \(0.3\times\) per concurrent client; this slowdown
is a result of the peak throughput of a single metadata server, which we found
to be about 3000 operations per second}.  The trade-off for better performance
is memory consumption because a larger
\oldcomment{segment}\newcomment{dispatch} size uses more space for buffering.
When journaling is on, the metadata server periodically stops serving requests
to flush ({\it i.e.} apply journal updates) to the metadata store.  The journal
overhead is sufficient enough to slow down metadata throughput but not so much
as to overwhelm the bandwidth of the object store.

@@

\textbf{CephFS Design}: Capabilities keep metadata strongly
consistent. To reduce the number of RPCs needed for consistency, clients can
obtain capabilities for reading and writing inodes, as well as caching reads,
buffering writes, changing the file size, and performing lazy IO.

% inode cache - reduces RPCs (lookups for create, readdirs for stats)
To keep track of the read caching and write buffering capabilities, the clients
and metadata servers agree on the state of each inode using an inode cache.  If
a client has the directory inode cached it can do metadata writes ({\it e.g.},
create) with a single RPC. If the client is not caching the directory inode
then it must do an extra RPC to determine if the file exists.  Unless the
client immediately reads all the inodes in the cache ({\it i.e.} \texttt{ls
-alR}), the inode cache is less useful for create-heavy workloads.

@@

\oldcomment{The benefits of caching the directory inode when creating
files}\newcomment{The cause for this slowdown} is shown in
Figure~\ref{fig:overhead-c}. The colors show the behavior of the client for two
different runs.  If only one client is creating files in a directory
(``isolated" curve on \(y1\) axis) then that client can lookup the existence of
new files locally before issuing a create request to the metadata server. If
another client starts creating files in the same directory then the directory
inode transitions out of read caching and the first client must send
\texttt{lookup()}s to the metadata server (``interfere" curve on \(y2\) axis).
These extra requests increase the throughput of the ``interfere" curve on the
\(y1\) axis because the metadata server can handle the extra load but
performance suffers.

>>>>

In our examination of the overheads of POSIX IO we benchmark and analyze
CephFS, the file system that uses Ceph's object store ({\it i.e.} RADOS) to
store its data and metadata. \newcomment{In this paper, ``client" is a storage
client or application that interacts with the metadata server, ``administrator"
is a system administrator that configures the storage, and ``end-users"
interact with the file system via home directories or runtimes.} To show how
the file system behaves under high metadata load we use a create-heavy
workload.  During this process we discovered, based on the analysis and
breakdown of costs, that durability and consistency have high overhead but we
urge the reader to keep in mind that this file system is an implementation of
one set of design decisions and our goal here is to highlight the effect that
those decisions have on performance.

%The RPCs are also serialized because the
%metadata server is single threaded; although na\"{\i}ve, this design is common
%because of the complexity of multi-threaded metadata
%servers~\cite{konstantinos:pdsw2014-lustre-metadata}.  
In this section we quantify the costs of consistency and durability in CephFS.
At the end of each subsection we compare the approach to ``decoupled
namespaces", the technique in related work that detaches subtrees from the
global namespace to relax consistency/durability guarantees. We use a
create-heavy workload for this study because it has high resource utilization,
as shown by the trace of compiling the Linux kernel in a CephFS mount in
Figure~\ref{fig:overhead-creates}.  The \texttt{untar} phase, which is
characterized by many creates, has the highest resource usage (combined CPU,
network, and disk) on the metadata server because of the number of RPCs needed
for consistency and durability.

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.32\linewidth}
      \centering
      \includegraphics[width=1\linewidth]{graphs/slowdown-journal.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/baseline-durability/visualize/viz.ipynb}{source}]
      effect of journal} \label{fig:overhead-a}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
      \centering
      \includegraphics[width=0.98\linewidth]{graphs/slowdown-interfere-scale.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/baseline-creates/visualize/viz.ipynb}{source}]
      interference hurts variability}
      \label{fig:overhead-b}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
      \centering
      \includegraphics[width=1.15\linewidth]{graphs/behavior-interfere.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/baseline-interfere/visualize/viz.ipynb}{source}]
      interference increases RPCs}
      \label{fig:overhead-c}
  \end{subfigure}
  \caption{\newcomment{The durability and strong consistency slowdown of the
existing CephFS implementation increases as the number of clients scales.
Results in (a) and (b)  are normalized to 1 client that creates 100K files in
isolation.  (a) shows the effect of journaling metadata updates; ``segment(s)"
is the number of journal segments dispatched to disk at once. (b) shows the
slowdown when another client interferes by creating files in all directories
and (c) highlights the cause: }\oldcomment{The overhead of durability and
strong consistency in CephFS. (a) shows the effect of different journal segment
sizes, which are streamed into the object store for fault tolerance. (b) and
(c) show that} when another client interferes, capabilities are revoked and
metadata servers do more work.} \label{fig:overhead}
\end{figure*}

@@

% - sequential IO, trim redundant operations
\textbf{CephFS Design}: A journal of metadata updates that streams into the
resilient object store. Similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL} the metadata journal is designed to be large (on
the order of MBs) which ensures (1) sequential writes into the object store and
(2) the ability for daemons to trim redundant or irrelevant journal entries.
The journal is striped over objects where multiple journal updates can reside
on the same object. There are two tunables\newcomment{, related to groups of
journal events called segments,} for controlling the journal: the segment size
and the dispatch size ({\it i.e.} the number of segments that can be dispatched
at once).  Unless the journal saturates memory or CPU resources, larger values
for these tunables result in better performance.

@@

% Effects on performance
Figure~\ref{fig:overhead-a} shows the effect of journaling with different
\oldcomment{segment sizes; the larger the segment size the bigger that the
writes into the object store are}\newcomment{dispatch sizes, normalized to 1
client that creates 100K files with journaling off (about 654 creates/sec). In
this case a dispatch size of 10 degrades performance the most because the
metadata server is overloaded with requests and cannot spare cycles to manage
concurrent segments.  Tuning and parameter sweeps show that a dispatch size of
10 is the worst and that larger sizes approach a dispatch size of 1; for all
future journal experiments we use a dispatch size of 40 which is a more
realistic configuration.  Although the ``no journal" curve appears flat, it is
actually a slowdown of about \(0.3\times\) per concurrent client; this slowdown
is a result of the peak throughput of a single metadata server, which we found
to be about 3000 operations per second}.  The trade-off for better performance
is memory consumption because a larger
\oldcomment{segment}\newcomment{dispatch} size uses more space for buffering.
\oldcomment{When journaling is on, the metadata server periodically stops serving requests
to flush ({\it i.e.} apply journal updates) to the metadata store.  The journal
overhead is sufficient enough to slow down metadata throughput but not so much
as to overwhelm the bandwidth of the object store.}

@@

% inode cache - reduces RPCs (lookups for create, readdirs for stats)

\textbf{CephFS Design}: Capabilities keep metadata strongly consistent. To
reduce the number of RPCs needed for consistency, clients can obtain
capabilities for reading and writing inodes, as well as caching reads,
buffering writes, changing the file size, and performing lazy IO.  To keep
track of the read caching and write buffering capabilities, the clients and
metadata servers agree on the state of each inode using an inode cache.  If a
client has the directory inode cached it can do metadata writes ({\it e.g.},
create) with a single RPC. If the client is not caching the directory inode
then it must do an extra RPC to determine if the file exists.  Unless the
client immediately reads all the inodes in the cache ({\it i.e.} \texttt{ls
-alR}), the inode cache is less useful for create-heavy workloads.

@@

\oldcomment{The benefits of caching the directory inode when creating
files}\newcomment{The cause for this slowdown} is shown in
Figure~\ref{fig:overhead-c}. The colors show the behavior of the client for two
different runs.  If only one client is creating files in a directory
(``no interference" curve on \(y1\) axis) then that client can lookup the existence of
new files locally before issuing a create request to the metadata server. If
another client starts creating files in the same directory then the directory
inode transitions out of read caching and the first client must send
\texttt{lookup()}s to the metadata server (``interference" curve on \(y2\) axis).
These extra requests increase the throughput of the ``interference" curve on the
\(y1\) axis because the metadata server can handle the extra load but
performance suffers.

### 2018-01-08 paper/sections/4_methodology.tex
paper: misc touch ups to address #40 and #48
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: typos
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb]
\centering
%\includegraphics[width=50mm]{figures/fig-decouple.png}
\includegraphics[width=1.0\linewidth]{figures/fig-decouple.png}
\caption{Illustration of the \textbf{mechanisms} used by applications to build
consistency/durability semantics. Descriptions are provided in by the
underlined words in Section~\S\ref{sec:the-cudelesfs-mechanisms}.
}\label{fig:decouple}
\end{figure}

@@

In this section we describe our API and framework that lets
\oldcomment{users}\newcomment{administrators} assign consistency and durability
semantics to subtrees in the global namespace. A \textbf{mechanism} is an
abstraction and basic building block for constructing consistency and
durability guarantees. Cudele exposes these mechanisms and the
\oldcomment{users}\newcomment{administrator} composes them together to
construct \textbf{policies}.  These policies are assigned to subtrees and they
dictate how the file system should handle operations within that subtree.
Below, we describe the mechanisms (which are \underline{underlined}), the
policies, and the API for assigning policies to subtrees.

@@

\subsubsection{Mechanisms Used for Durability} \underline{Stream} is one of the
mechanisms used by default in CephFS.  Using existing configuration settings in
Ceph we can turn Stream on and off.  If it is off, then the metadata servers
will not save journals in the object store. For \underline{Local Persist}, clients write
serialized log events to a file on local disk and for \underline{Global Persist},
clients push the journal into the object store. The overheads for both Local
Persist and Global Persist is the write bandwidth of the local disk and
object store, respectively.  These persist mechanisms are part of the library that
links into the client.

@@

% which system they represent and which are impossible
Existing, state-of-the-art systems in HPC can be represented by the cells in
Table~\ref{table:spectrum} (we construct the semantics for these systems later
in Section~\S\ref{sec:microbenchmarks}).  POSIX IO-compliant systems like
CephFS and IndexFS have global consistency and durability\footnote{ IndexFS
also has bulk merge which is a form of ``weak consistency"}; DeltaFS uses
``invisible" consistency and ``local" durability and BatchFS uses ``weak"
consistency and ``local" durability. These systems have other features that
could push them into different semantics but we assign labels here based on the
points emphasized in the papers.  To compose the mechanisms
\oldcomment{users}\newcomment{administrators} inject which mechanisms to run
and which to use in parallel using a domain specific language.  Although we can
achieve all permutations of the different guarantees in
Table~\ref{table:spectrum}, not all of them make sense. For example, it makes
little sense to do \texttt{append client journal+RPCs} since both mechanisms do
the same thing or \texttt{stream+local persist} since ``global" durability is
stronger and has more overhead than ``local" durability. The cost of each
mechanism and the semantics described above are quantified in
Sections~\S\ref{sec:microbenchmarks} and~\S\ref{sec:use-case-1}.

% talk of eventual consistency
The consistency and durability properties in Table~\ref{table:spectrum} are not
guaranteed until all mechanisms in the cell are complete. The compositions
should be considered atomic and there are no guarantees while transitioning
between policies. For example, updates are not deemed to have ``global"
durability until they are safely saved in the object store. If a failure occurs
during Global Persist or if we inject a new policy that changes a subtree from
Local Persist to Global Persist, Cudele makes no guarantee until the mechanisms
are complete. Despite this, production systems that use Cudele should state
up-front what the transition guarantees are for subtrees.

@@

% the interface
Users control consistency and durability for subtrees by contacting a daemon in
the system called a monitor, which manages cluster state changes.  Users
present a directory path and a policies configuration that gets distributed and
versioned by the monitor to all daemons in the system. For example,
(msevilla/mydir, policies.yml) would decouple the path ``msevilla/mydir" and
would apply the policies in ``policies.yml".  The policies file supports the
following parameters (default values are in parenthesis): which consistency
model to use (\texttt{RPCs}), which durability model to use (\texttt{stream})
number of inodes to provision to the decoupled namespace (100), which interfere
policy to use, {\it i.e.} how to handle a request from another client
targeted at this subtree (\texttt{allow}). The ``Consistency" and ``Durability"
parameters are compositions of mechanisms; they can be serialized (\(+\)) or
run in parallel (\(|\|\)).  ``Allocated Inodes" is a way for the application to
specify how many files it intends to create. It is a contract so that the file
system can provision enough resources for the incumbent merge and so it can
give valid inodes to other clients. The inodes can be used anywhere within the
decoupled namespace ({i.e.} at any depth in the subtree).  ``Interfere Policy"
has two settings: \texttt{block} and \texttt{allow}.  For \texttt{block}, any
requests to this part of the namespace returns with ``Device is busy", which
will spare the metadata server from wasting resources for updates that may get
overwritten. If the application does not mind losing updates, for example it
wants approximations for results that take too long to compute, it can select
\texttt{allow}. In this case, metadata from the interfering client will be
written and the computation from the decoupled namespace will take priority at
merge time because the results are more accurate.  Given these default values
decoupling the namespace with an empty policies file would give the application
100 inodes but the subtree would behave like the existing CephFS
implementation.

>>>>

\begin{figure}[tb]
\centering
%\includegraphics[width=50mm]{figures/fig-decouple.png}
\includegraphics[width=1.0\linewidth]{figures/fig-decouple.png}
\caption{Illustration of the \textbf{mechanisms} used by applications to build
consistency/durability semantics. Descriptions are provided by the
underlined words in Section~\S\ref{sec:the-cudelesfs-mechanisms}.
}\label{fig:decouple}
\end{figure}

@@

In this section we describe our API and framework that lets
\oldcomment{users}\newcomment{administrators} assign consistency and durability
semantics to subtrees in the global namespace. A \textbf{mechanism} is an
abstraction and basic building block for constructing consistency and
durability guarantees.\oldcomment{Cudele exposes these mechanisms and the
users}\newcomment{ The administrator} composes these mechanisms together to
construct \textbf{policies}.  These policies are assigned to subtrees and they
dictate how the file system should handle operations within that subtree.
Below, we describe the mechanisms (which are \underline{underlined}), the
policies, and the API for assigning policies to subtrees.

@@

\subsubsection{Mechanisms Used for Durability} \underline{Stream} is one of the
mechanisms used by default in CephFS.  Using existing configuration settings we
can turn Stream on and off.  If it is off, then the metadata servers will not
save journals in the object store. For \underline{Local Persist}, clients write
serialized log events to a file on local disk and for \underline{Global
Persist}, clients push the journal into the object store. The overheads for
both Local Persist and Global Persist is the write bandwidth of the local disk
and object store, respectively.  These persist mechanisms are part of the
library that links into the client.

@@

% which system they represent and which are impossible
Existing, state-of-the-art systems in HPC can be represented by the cells in
Table~\ref{table:spectrum} POSIX IO-compliant systems like CephFS and IndexFS
have global consistency and durability\footnote{ IndexFS also has bulk merge
which is a form of ``weak consistency"}; DeltaFS uses ``invisible" consistency
and ``local" durability and BatchFS uses ``weak" consistency and ``local"
durability. These systems have other features that could push them into
different semantics but we assign labels here based on the points emphasized in
the papers.  To compose the mechanisms
\oldcomment{users}\newcomment{administrators} inject which mechanisms to run
and which to use in parallel using a domain specific language.  Although we can
achieve all permutations of the different guarantees in
Table~\ref{table:spectrum}, not all of them make sense. For example, it makes
little sense to do \texttt{append client journal+RPCs} since both mechanisms do
the same thing or \texttt{stream+local persist} since ``global" durability is
stronger and has more overhead than ``local" durability. The cost of each
mechanism and the semantics described above are quantified in
Sections~\S\ref{sec:microbenchmarks}.

% talk of eventual consistency
In our prototype, the consistency and durability properties in
Table~\ref{table:spectrum} are not guaranteed until all mechanisms in the cell
are complete. The compositions should be considered atomic and there are no
guarantees while transitioning between policies. For example, updates are not
deemed to have ``global" durability until they are safely saved in the object
store. If a failure occurs during Global Persist or if we inject a new policy
that changes a subtree from Local Persist to Global Persist, Cudele makes no
guarantee until the mechanisms are complete. Despite this, production systems
that use Cudele should state up-front what the transition guarantees are for
subtrees. This is not a limitation of our approach; it just lead to the
simplest implementation.

@@

% the interface
Users control consistency and durability for subtrees by contacting a daemon in
the system called a monitor, which manages cluster state changes.  Users
present a directory path and a policies configuration that gets distributed and
versioned by the monitor to all daemons in the system. For example,
(msevilla/mydir, policies.yml) would decouple the path ``msevilla/mydir" and
would apply the policies in ``policies.yml".  The policies file supports the
following parameters (default values are in parenthesis): which consistency
model to use (\texttt{RPCs}), which durability model to use (\texttt{stream}), 
number of inodes to provision to the decoupled namespace (100), and which interfere
policy to use, {\it i.e.} how to handle a request from another client
targeted at this subtree (\texttt{allow}). The ``Consistency" and ``Durability"
parameters are compositions of mechanisms; they can be serialized (\(+\)) or
run in parallel (\(|\|\)).  ``Allocated Inodes" is a way for the application to
specify how many files it intends to create. It is a contract so that the file
system can provision enough resources for the incumbent merge and so it can
give valid inodes to other clients. The inodes can be used anywhere within the
decoupled namespace ({\it i.e.} at any depth in the subtree).  ``Interfere Policy"
has two settings: \texttt{block} and \texttt{allow}.  For \texttt{block}, any
requests to this part of the namespace returns with ``Device is busy", which
will spare the metadata server from wasting resources for updates that may get
overwritten. If the application does not mind losing updates, for example it
wants approximations for results that take too long to compute, it can select
\texttt{allow}. In this case, metadata from the interfering client will be
written and the computation from the decoupled namespace will take priority at
merge time because the results are more accurate.  Given these default values
decoupling the namespace with an empty policies file would give the application
100 inodes but the subtree would behave like the existing CephFS
implementation.

### 2018-01-08 paper/sections/5_implementation.tex
paper: typos
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

We use a programmable storage approach~\cite{sevilla:eurosys17} to design
Cudele; namely, we try to leverage components inside Ceph to inherit the
robustness and correctness of the internal subsystems. Using this `dirty-slate'
approach, we only had to implement 4 of the 6 mechanisms from
Figure~\ref{fig:decouple} and just 1 required changes to the underlying storage
system itself.  In this section, we first describe a Ceph internal subsystem or
component and then we show how we use it in Cudele.

@@

In CephFS, the metadata store is a data structure that represents the file
system namespace. This data structure is stored in two places: in memory ({\it
i.e.} in the collective memory of the metadata server cluster) and as objects
in the object store. In the object store, directories and their inodes are
stored together in objects to improve the performance of scans.  The metadata
store data structure is structured as a tree of directory fragments making it
easier to read and traverse. \textbf{In Cudele} the RPCs mechanism uses the
metadata store to service requests. Using code designed for recovery,
Nonvolatile Apply and Volatile Apply replay updates onto the metadata store in
memory and in the object store, respectively.  When the clients are ready to
merge their updates back into the global namespace, they pass a binary file of
metadata updates to the metadata server.

@@

In CephFS, inodes already store policies, like how the file is striped across
the object store or for managing subtrees for load balancing. These policies
adhere to logical partitionings of metadata or data, like Ceph pools and file
system namespace subtrees. To implement this, the namespace data structure has
the ability to recursively apply policies to subtrees and to isolate subtrees
from each other. \textbf{In Cudele} the large inodes store consistency and
durability policies in the directory inode. This approach uses the File Type
interface from the Malacology programmable store
system~\cite{sevilla:eurosys17} and it tells clients how to access the
underlying metadata. The underlying implementation stores executable code in
the inode that calls the different Cudele mechanisms. Of course, there are many
security and access control aspects of this approach but that is beyond the
scope of this paper.

>>>>

We use a programmable storage approach~\cite{sevilla:eurosys17} to design
Cudele; namely, we try to leverage components inside CephFS to inherit the
robustness and correctness of the internal subsystems. Using this `dirty-slate'
approach, we only had to implement 4 of the 6 mechanisms from
Figure~\ref{fig:decouple} and just 1 required changes to the underlying storage
system itself.  In this section, we first describe a CephFS internal subsystem or
component and then we show how we use it in Cudele.

@@

In CephFS, the metadata store is a data structure that represents the file
system namespace. This data structure is stored in two places: in memory ({\it
i.e.} in the collective memory of the metadata server cluster) and as objects
in the object store. In the object store, directories and their inodes are
stored together in objects to improve the performance of scans.  The metadata
store data structure is structured as a tree of directory fragments making it
easier to read and traverse. \textbf{In Cudele} the RPCs mechanism uses the
metadata store to service requests. Using code designed for recovery,
Volatile Apply and Nonvolatile Apply replay updates onto the metadata store in
memory and in the object store, respectively.  When the clients are ready to
merge their updates back into the global namespace, they pass a binary file of
metadata updates to the metadata server.

@@

In CephFS, inodes already store policies, like how the file is striped across
the object store or for managing subtrees for load balancing. These policies
adhere to logical partitionings of metadata or data, like Ceph pools and file
system namespace subtrees. To implement this, the namespace data structure has
the ability to recursively apply policies to subtrees and to isolate subtrees
from each other. \textbf{In Cudele} the large inodes also store consistency and
durability policies. This approach uses the File Type
interface from the Malacology programmable storage
system~\cite{sevilla:eurosys17} and it tells clients how to access the
underlying metadata. The underlying implementation stores executable code in
the inode that calls the different Cudele mechanisms. Of course, there are many
security and access control aspects of this approach but that is beyond the
scope of this paper.
